Probability Aggregation in Time-Series: Dynamic Hierarchical Modeling of Sparse Expert Beliefs

### 2014-01-31 Revision/Response/response.tex

\textbf{The extant literature doesn’t address the issue of dynamic aggregation over time.  The combination methods developed in the literature won’t be able to do justice to evolving expert opinions over time as they will treat them as one combination problem at a given point of time.  Also, the small no. of expert forecasts at any given time would make the combined forecast at a given time weak.  The alternative is to borrow strength from past forecasts in a sensible way – which is explored in the present paper. }

\textbf{The other contribution of the paper is study various groups of experts based on their self-assessed expertise. The parameters used in the framework directly lend themselves to the study of group specific over-confidence/under-confidence, disagreement between experts, question difficulty and evolving expert opinions.   The combined forecast is shown to be empirically calibrated and sharp.   The estimation involves two stages a sample step and a calibrate step. In the sample step the model parameters are sampled using a Gibbs sampling paradigm. In the calibrate step a one –parameter optimization is used to calibrate the experts forecasts with the truth using a proper scoring rule.}

\textbf{The methodology presented in the paper for combination has been compared against simple exponentially weighted generalizations of existing methods like equally weighted probability forecasts and the beta-transformed probability forecast method proposed by Ranjan and Gneiting (2010).  However, these generalizations have been restricted to single combination parameters only. One wonders why these methods were not generalized to include group specific combination parameters. This seems to me the natural thing to do otherwise, the comparison to other methods won’t be fair.}\\
Given that EWMLA already includes group specific combination parameters, only EWMA and EWMLA need to be generalized. In the revised manuscript EWMA and EWMLA make use the expertise information by incorporating a weighted mean (instead of the simple equally weighted mean used in the previous version) of the forecasts. The results, however, look very similar.\\
\\

\textbf{Another limitation of the present work is that it masks question specific and individual specific bias terms and only estimates group specific bias irrespective of question and individual.   This won’t allow one to understand any outcome specific bias that may exist in the groups or individuals.  For example certain geo-political outcomes may be more desirable for people in general and individuals might be biased for that outcome.  It would be interesting to see if authors can come up with an framework in which bias can be studied at multiple levels, be it question/ outcome specific, individual specific or group of experts specific or even time-specific.  The present work only looks at group specific bias.  Perhaps a hierarchical approach to bias decomposition may be more suitable.}\\
We have added a sub-section called \textit{Bias Structure} that discusses a hierarchical approach to bias decomposition. In this subsection we briefly explain how the bias can be estimated at  question-specific and individual-specific. An extension to a time-specific bias structure is briefly mentioned in the conclusion.
\\

\textbf{Overall I am happy with the work as it explores a difficult and unexplored problem and offers some directions.  The modeling of the problem exposes various parameters which have an intuitive interpretation for the researcher and helps understand the expert opinions better.  However I would like to see the authors update Table-3 with group specific parameters used for other methods as well (in particular, EWMA, EWMBA, EWMLA).  Also, I would like to see some discussion on how bias (under-forecasting and over-forecasting) can be estimated and studied more generally at multiple levels – individuals, questions, groups and even time specific.}
\\

\clearpage
\section*{\Large Referee 3}
\textbf{This manuscript describes a model for aggregating probabilities judgements made by experts. It allows for the experts to update their beliefs at different points in time and it allows for different biases between different groups of experts. The general idea is very interesting, but the implementation is lacking. The model makes strong, simplistic assumptions, and the applicability in practice is questionable.}
\\
\\
\textbf{General Comments}
\begin{enumerate}
\item \textbf{The manuscript is generally well-written, but it is way too long. The writing is too leisurely throughout, and many issues and concepts are unnecessarily discussed two or more times.}\\
The paper is now much shorter. We have moved material to the Online Supplement, removed some of the unnecessary sections and graphs, and cut many redundancies.\\

\item \textbf{In my opinion, the model is unnecessarily simplistic. The authors assume that experts are indistinguishable beyond (self-reported!) expertise. Bias and variance in their forecasts are assumed to be constant over experts, questions, and time. The authors fit a Bayesian hierarchical model that would allow for sophisticated shrinkage and borrowing of strength between experts and between questions, but this is basically not exploited in the model at all. In fact, the authors claim (incorrectly) that estimating a bias term separately for each expert is not possible. For example, why not specify a prior for the ith expert’s bias such as $\beta_i | b_{j(i)},\sigma_2 \sim N(b_{j(i)},\sigma^2)$, where $j(i)$ is the group membership of the $i$th expert?}\\
Thank you for pointing this out. We have added a brief subsection that discusses question-specific and individual-specific bias structures. The choice made in this paper was partly driven by our real-world dataset and the preference of the social scientists working with it. One goal of this paper is to describe a basic framework that can be extended rather easily for any such analysis. \\

\item \textbf{ I wonder how applicable this methodology actually is in practice. While I cannot comment on how interesting the fitted model parameters are to social scientists in terms interpreting things like question difficulty, the results to me offer little in terms of interpretation beyond what would have been clear from the outset or what can be learned from simple plots of the data.
\\
What I consider the most interesting is to make predictions for future events, which I am not sure is really possible in real-world situations using the model. Since the methodology is retrospective (i.e., you do not do on-line, filtering inference as I think would be more appropriate), it seems to be necessary to wait until a large study like the one described has been completed, with all outcomes having been observed. Then, you can fit the model. Only after this can the methodology be used to make forecasts for other, future events of interest, but it is not clear that a similar data situation could arise, and even if so, if the assumptions and parameters from your fitted model are still applicable to this new situation. For example, are the new experts comparable to the old ones? Since there seem to be large differences in question difficulties, what difficulty does a particular new question have?}\\
The model is interesting for three different reasons:
\begin{enumerate}
\item Model inference: This is inherently interesting to social scientist.
\item Time-Forward Forecasting: Our methodology does not take long to fit in a retrospect fashion. Once the estimates have been obtained, the estimate of the final hidden state can be propagated forward. We have included a paragraph about this in the revised version of the paper.
\item Aggregating at Current Time Point: The goal is to obtain the ``best" probability estimate given all the information available now. This is the most interesting to social sciences as it reflects the current consensus about the event and its associated uncertainty. This is what our model was built to address. We evaluate this ability in our out-of-sample aggregation section.
\end{enumerate}
The new experts tend to be very similar to new ones. They do not need to be the same individuals as long as they, as a group, look similar. In terms of determining the difficulty of a new problem, this is an active and very difficult research problem. One can use old questions to model the difficulty. With no information but the description of the problem, the best one can do is to assign the new problem an average difficulty level.

\end{enumerate}

\textbf{Specific Comments}
\begin{enumerate}
\item \textbf{p. 2: The punctuation seems to be off in the second part of the second paragraph.}\\
This has been corrected.\\

\item \textbf{p. 6: Can you explain why it is reasonable to assume that the forecast maximizes sharpness subject to calibration? Also, in Definition 2, it seems like p, q, and p0 are all fixed numbers on the unit interval, so I am not sure with respect to which random variables the expectations are meant to be taken.}\\
$logit^{-1}(X_{t,k})$ represents the ``best" forecast under all the relevant information available at time $t$. This is an idealized forecast that should be assumed to be well-calibrated. Furthermore, given that it is based on all the information available, it ought to be as close to 0 or 1 as possible; that is, as sharp as possible. Due to the editor's suggestions, the technical definitions have been removed. 
\\

\item \textbf{p. 7: Instead of writing “drifts to inifity,” I think things would be more easily understandable if you wrote “drifts to positive or negative infinity."}\\
 This has been corrected.\\

\item \textbf{p. 8: For completeness, you should briefly mention in the main text which parameters are assumed to be random and what their priors are. Also, even after reading the appendix, it is still not clear to me what you mean by “parameter estimates.” All you are obtaining with the Gibbs sampler are samples from the posterior distribution. A loss function would be needed to obtain (point) estimates of the parameters.}\\
 We added ``Therefore the parameters of the model are $\boldsymbol{b}$, $\sigma^2_k$, $\gamma_k$, and $\tau^2_k$ for $k = 1, \dots, K$. Their prior distributions are chosen to be non-informative,  $p(\boldsymbol{b}, \sigma^2_k| \boldsymbol{X}_k) \propto \sigma^2_k$ and $p(\gamma_k, \tau^2_k| \boldsymbol{X}_k) \propto \tau^2_k$." and "These estimates are obtained by first computing a posterior sample via Gibbs sampling and then taking the average of the posterior sample."
\\

\item \textbf{p. 10: While the simulated data are not generated exactly from your model, it does seem like the data-generating model is much closer to your model then to the model underlying EWMA.}\\
The underlying mechanism to generate the hidden states is very different from the one given in our dynamic linear model. The only similarity is in how the noise and bias are added to the hidden states. The noise in this case has mean zero and can be reduced by averaging. Therefore if the model can determine the bias terms accurately; that is, determine the extent to which each expertise group should be shifted for improved calibration, the model's performance ought to be very good.

Notice that this section has been updated to include an expertise-weighted version of EWMA. This procedure uses 6 parameters to calibrate the group-specific average probabilities. This is a much more flexible calibration function than the one in our SAC model. It is therefore expected that under an easy forecasting setup, such as the one in our paper, EWMA performs better than SAC. It is not entirely clear whether this comparison is completely fair. It serves, however, only a sanity check. The more important comparison is done under the real-world data. 
\\

\item  \textbf{p. 11: EWMA should be defined here, not much later in the manuscript.}\\
 The definition of EWMA has been moved.\\

\item \textbf{p. 12: EWMA outperforms SAC roughly when $\beta \in [.95, 1.5]$, which in my opinion does not correspond to a “very small” bias. If I understand correctly, $\beta = 1$, for example, actually means that the bias varies from 0.5 to 2.}\\
That is correct: $\beta$ is a multiplier for the vector $[1/2, 3/4, 1, 4/3, 2/1]$. When $\beta  = 1$, the average bias among the experts is around 1.12. This bias is not very large.
\\
\item \textbf{p. 14: Why is the SDLM model not hierarchical? The process model can clearly be written in a hierarchical way, and there are also parameters that (I believe) have prior distributions.}\\
We wanted to say that the model does not have any parameters that are shared across different questions. This has now been changed to "Given that this model does not share any parameters across different questions, estimates of the hidden process can be obtained directly for the questions in the testing set without fitting the model first on the training set."\\

\item \textbf{p. 14/15: For all models, how did you choose the number of iterations in the Gibbs sampler? Should the number of MCMC iterations be larger for the fully Bayesian model, since the hidden state is sampled using the Metropolis algorithm? By the way, if you assumed a probit-link instead of a logit-link, the full conditional distributions are available in closed form and no Metropolis steps are necessary.}\\
We have added: "Before introducing the competing models, note that all choices of thinning and burn-in made in this section are conservative and have been made based on pilot runs of the models.  This was done to ensure a posterior sample that has low autocorrelation and arises from a converged chain." The number of iterations for the fully Bayesian model should be a bit larger. We first made choices for this model and then used the same choice for SAC.
\end{enumerate}

\bibliographystyle{imsart-nameyear}
\bibliography{biblio}		% expects file "myrefs.bib"

\end{document}
